---
title: "Weight of Fish"
author: "Kaylie Fagoaga"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}


if(!require("Bolstad")) {install.packages("Bolstad");require("Bolstad")}
```



## Perch

### Best Models

```{r}
perchModel=lm(Weight~ .,data=Perch)
summary.lm(perchModel) 
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model
```{r}
perch2=lm(Weight~Height+Width, data=Perch)
summary.lm(perch2)
```

The best two regressor models to predict Weight is Height + Width. 

## Pike

### Best Models
```{r}
pikeModel=lm(Weight~ .,data=Pike)
summary.lm(pikeModel) 
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model
```{r}
Pike2=lm(Weight~Length1+Length3, data=Pike)
summary.lm(Pike2)
```

The best two regressor models to predict Weight is Length1 + Length3.

## Roach

### Best Models
```{r}
roachModel=lm(Weight~ .,data=Roach)
summary.lm(roachModel) 
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

### Best Two regressor model
```{r}
Roach2=lm(Weight~Length3+Width, data=Roach)
summary.lm(Roach2)
```

The best two regressor models to predict Weight is Length3 + Width.

## Final Summary Statements

The best regressor models in Perch to predict Weight is Height and Width. 

The best regressor models in Pike to predict Weight is Length1 and Length3.    

The best regressor models in Roach to predict Weight is Length3 and Width. 
